---
title: "Plant Protein Combined Surveys"
format:
  dashboard:
    sidebar:
      collapse: true
scrolling: true
include-in-header:
  text: |
    <link rel="shortcut icon" href="/assets/images/logos/b2flogo.png" />
    <link rel="icon" type="image/x-icon" href="/assets/images/logos/favicon.ico">
    <link rel="stylesheet" type="text/css" href="styles.css">
    <script src="scripts.js"></script>
---

```{r}
source("pp_combined.R")
source("bcs.R")
```


# Summary

## Row {height="220px"}

### Column

::: {.valuebox icon="bar-chart-steps" color="secondary" title="Industry Confidence"}

`r curr_ic`

`r curr_ic_deltas_html`

<i class="bi bi-info-circle info-icon" tabindex="0" data-bs-trigger="focus" data-bs-toggle="popover" data-bs-placement="top" data-bs-content="`r curr_ic_tooltip`"></i>

:::


### Column

::: {.valuebox icon="cloud-sun" color="secondary" title="Business Uncertainty"}

`r curr_bu`

`r curr_bu_deltas_html`

<i class="bi bi-info-circle info-icon" tabindex="0" data-bs-trigger="focus" data-bs-toggle="popover" data-bs-placement="top" data-bs-content="`r curr_bu_tooltip`"></i>
  
:::


### Column

::: {.valuebox icon="people" color="light" title="Employment Outlook"}

`r curr_eo`

`r curr_eo_deltas_html`

<i class="bi bi-info-circle info-icon" tabindex="0" data-bs-trigger="focus" data-bs-toggle="popover" data-bs-placement="top" data-bs-content="`r curr_eo_tooltip`"></i>

:::


## Row

### Column {.tabset}
```{r}
#| title: "Business Uncertainty"
uncertainty_bar
```

::: {.card title="Latest Period"}
<div class="mt-5 text-center">
<span class="display-1">`r curr_bu`</span>

`r curr_bu_deltas_html_na`

<span class="text-muted small m-5 p-4">`r bu_text`</span>
</div>
:::

::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

### Column {.tabset}
```{r}
#| title: "3-Year Business Plans"
plans_pie
```

```{r, results='asis'}
#| title: "Latest Period"
cat(plans_nb_html)
```

::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

## Row

### Column {.tabset}
```{r}
#| title: "Competitive Position"
comp_past_3_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(comp_past_3_nb_html)
```

::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::


### Column
```{r}
#| title: "Regional Sales Distribution"
regions_dist_donut
```


# Production & Orders

## Row

### Column {.tabset}

```{r}
#| title: "Recent Orders"
orders_past_3_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(orders_past_3_nb_html)
```

::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

### Column {.tabset}

```{r}
#| title: "Current Order Books"
orders_curr_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(orders_curr_nb_html)
```

::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

## Row

### Column {.tabset}

```{r}
#| title: "Production Level"
prod_lvl_box
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

### Column {.tabset}

```{r}
#| title: "Production Capacity"
prod_cap_pie
```

```{r, results='asis'}
#| title: "Latest Period"
cat(prod_cap_nb_html)
```

::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

## Row {.tabset}

```{r}
#| title: "Current Stocks of Finished Products"
stocks_curr_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(stocks_curr_nb_html)
```

::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

## Row

### Column {.tabset}

```{r}
#| title: "Recent Production"
prod_past_3_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(prod_past_3_nb_html)
```

::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

```{r}
#| title: "Euro Area Historical"
# bcs_m_ea_prod_trend
```
### Column {.tabset}

```{r}
#| title: "Production Expectations"
prod_next_3_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(prod_next_3_nb_html)
```

::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::


## Row {.tabset}

```{r}
#| title: "Factors Limiting Production"
prod_limits_bar
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

# Inputs & Prices

## Row

### Column {.tabset}

```{r}
#| title: "Recent Input Costs"
costs_past_3_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(costs_past_3_nb_html)
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

### Column {.tabset}

```{r}
#| title: "Expected Input Costs"
costs_next_3_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(costs_next_3_nb_html)
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

## Row

### Column {.tabset}

```{r}
#| title: "Recent Selling Prices"
prices_past_3_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(prices_past_3_nb_html)
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

### Column {.tabset}

```{r}
#| title: "Expected Selling Prices"
prices_next_3_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(prices_next_3_nb_html)
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

# Labour

## Row

### Column {.tabset}

```{r}
#| title: "Recent Staff Numbers"
emp_past_3_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(emp_past_3_nb_html)
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

### Column {.tabset}

```{r}
#| title: "Expected Staff Numbers"
emp_next_3_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(emp_next_3_nb_html)
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

## Row

### Column {.tabset}

```{r}
#| title: "Recent Labour Costs"
lab_costs_past_3_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(lab_costs_past_3_nb_html)
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

### Column {.tabset}
```{r}
#| title: "Labour Costs"
lab_costs_lvl_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(lab_costs_lvl_nb_html)
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

## Row {.tabset}

```{r}
#| title: "Finding Skilled Labour"
lab_skill_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(lab_skill_nb_html)
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::


# Investment & Innovation

## Row {.tabset}

```{r}
#| title: "Recent Investments"
inv_past_3_bar
```
```{r, results='asis'}
#| title: "Latest Period"
cat(inv_past_3_nb_html)
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

## Row

### Column {.tabset}

```{r}
#| title: "Current Year Investments"
inv_curr_y_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(inv_curr_y_nb_html)
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

### Column {.tabset}

```{r}
#| title: "Next Year Investment Expectations"
inv_next_y_pie
```
```{r, results='asis'}
#| title: "Latest Period"
cat(inv_next_y_nb_html)
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

## Row {.tabset}

```{r}
#| title: "Structure of Investments (Only asked in Q4)"
inv_structure
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

## Row {.tabset}

```{r}
#| title: "Drivers of Investments (Only asked in Q4)"
inv_drivers
```
::: {.card title="Time Series"}
<div class="mt-5 text-center">
Available in 2025-Q2...
</div>
:::

# Metadata

## Row {height="220px"}

```{r}
#| content: valuebox
#| title: "Latest Data Period"
list(
  icon = "calendar-check",
  color = "secondary",
  value = curr_period
)
```

::: {.valuebox icon="file-earmark-lock" color="secondary" title="Pre-Release Access"}

Dec. 2-8

<i class="bi bi-info-circle info-icon" 
   tabindex="0"
   data-bs-trigger="focus" 
   data-bs-toggle="popover" 
   data-bs-placement="top"
   data-bs-content="Only available to participating companies. <a href='https://research.bridge2food.com/surveys/#participating-companies'>Learn more</a>.">
</i>
:::

```{r}
#| content: valuebox
#| title: "Public Release"
list(
  icon = "universal-access-circle",
  color = "light",
  value = "Dec. 9"
)
```


## Row

::: {.card title="About"}

The Plant Protein Combined Surveys data dashboard displays aggregated data from three surveys covering five segments of the supply chain: 

* [Plant Protein Upstream Suppliers (PPUS) Survey](https://research.bridge2food.com/surveys/ppus)
  - Primary ingredients suppliers
  - Secondary ingredients suppliers
  - Equipment & technollgy suppliers
* [Plant Meat Producers (PMP) Survey](https://research.bridge2food.com/surveys/pmp)
* [Plant Dairy Producers (PDP) Survey](https://research.bridge2food.com/surveys/pdp)

### Current Period Segment Distribution

`r segments_pie`

For more information about this industry reporting and intelligence framework, visit [research.bridge2food.com/surveys](https://research.bridge2food.com/surveys/).

For questions, comments, or to express interest in participating in the framework in upcoming data periods, email research@bridge2food.com.

:::


::: {.card title="Understanding Net Balances"}

Many of the data and indicators presented in this dashboard are expressed as net balances.

The concept of net balance is often used in surveys, economic analysis, and business reporting to indicate the overall tendency or sentiment within a group by measuring the difference between positive and negative responses or changes. Net balance simplifies complex data by summarizing it as a single percentage figure, making trends or shifts more interpretable at a glance.

Net balance is typically calculated as the difference between the percentage of respondents (or data points) that report an increase or positive change and the percentage that report a decrease or negative change. 

**Interpreting Net Balance Figures**
<br>

**Positive Net Balance**: A positive net balance suggests that a larger proportion of respondents or data points are experiencing positive change than negative change. Higher positive values imply stronger net positivity.

**Negative Net Balance**: A negative net balance means that more respondents or data points report a negative change than a positive one. The further into negative territory, the stronger the net negative sentiment.

**Zero Net Balance**: A net balance close to zero (0%) suggests that positive and negative responses are roughly equal, indicating a neutral or balanced sentiment. This could mean stability, but it could also imply stagnation, depending on the context.

Net balance figures can range from -100 to 100, providing a standardized way to interpret sentiment or change, where the value’s position within this range shows the direction and strength of the net sentiment.
:::
  